Keep your Laziness in Check

### 2018-03-03 paper/main.tex
[paper] updates

We can write another executable specification for this property
of $\lk{solutionStep}_n$. Testing the implementation based on
strict maps also immediately produces a counter example.
%
\begin{inlinecode}
TODO: expectation-spec for solutionStep
\end{inlinecode}
%

@@

\paragraph*{Binary Search Trees}

\leo{data structures - code - short explanation}

\paragraph*{Characterizing Laziness}

\begin{itemize}
\item Specification of laziness - TreeD data structure \leo{Mention how it will be generically derived}
\item Strict / Spine-strict maps
\item Fully lazy map as a between spec
\end{itemize}

>>>>

We can write another executable specification for this property of
$\lk{solutionStep}_n$. To describe the concrete \textit{demand} on
maps, we need to first give a data type definition for \lk{Map}. We
choose a simple binary search tree representation here. We also define
a \lk{lookupD} function \hzh{we should probably move this to the
appendix} to lookup demand at a given key.
%
\begin{inlinecode}
data Map  k v = Bin (Map k v) k v (Map k v)
              | Empty

data MapD k v = BinD (Thunk (MapD k v)) (Thunk k) (Thunk v) (Thunk (MapD k v))
              | EmptyD

lookupD :: k -> MapD k v -> Thunk v
lookupD k EmptyD                          = T
lookupD k (BinD _ T      _ _)             = T
lookupD k (BinD l (E k') v r) | k == k'   = v
                              | k <= k'   = recur l
                              | otherwise = recur r
  where recur (E demand) = lookupD k demand
        recur T          = T
\end{inlinecode}
%
Now, we can write an executable specification
for \lk{solutionStep}. \hzh{TODO: write the spec with
strictCheckWithResults, and show a counterexample}
%
\begin{inlinecode}
\end{inlinecode}
%

@@

\section{Demand Types and Specification}
\label{sec:demand-types-and-spec}
\hzh{In this section, we should explain how demand types and specification work in general. We don't actually have to define a ListD/TreeD for every type out there. There is also a generic pattern for the type of a specification given the type of a function. We should also talk about the non-exact versions of specifications, and how they work}

\section{Generating lazy functions}
\label{sec:gen-lazy-fun}
\hzh{In this section, we should talk about how lazy functions are generated, and why QuickCheck's implementation doesn't generate lazy functions.}
